The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-03-10 papers/pair-correlation/paper.tex
Fixed a couple plot bugs Tested on paho-arch. Took 0:48.83.
Fixed plot axis labels Tested on paho-arch. Took 0:55.48.

%% The finalized form of our pair correlation function is:
%% \begin{align}
%%   g^{(2)}(\rr_1,\rr_2) = \frac{g(|r_{12}|, g_\sigma(\rr_1)) + g(|r_{12}|, g_\sigma(\rr_2))}{2}
%% \end{align}
%% \begin{figure}
%%   \centering
%%   \includegraphics[width=\columnwidth]{figs/ghs-g2}% \\
%%   %\includegraphics[width=\columnwidth]{figs/ghs-g-ghs}
%%   \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
%% \end{figure}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Remove one of, or make a note of, the two curves for this
      work}\fixme{Fix MC issue here (volume wrong?)} \fixme{Add backward curve
      for this work mc?}\fixme{z-axis wrong}The triplet
    distribution function $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3,
    plotted when $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding to the
    contact value of the \emph{pair} distribution function.  The plot on the
    right shows the value of $g^{(3)}$ along the path shown as a dotted line on
    the plot to the left.}\label{fig:triplet-contact-distribution}
\end{figure*}

>>>>

%% The finalized form of our pair correlation function is:
%% \begin{align}
%%   g^{(2)}(\rr_1,\rr_2) = \frac{g(|r_{12}|, g_\sigma(\rr_1)) + g(|r_{12}|, g_\sigma(\rr_2))}{2}
%% \end{align}
\pahosays{Was plotting the radial distribution function meant to be commented?}
%% \begin{figure}
%%   \centering
%%   \includegraphics[width=\columnwidth]{figs/ghs-g2}% \\
%%   %\includegraphics[width=\columnwidth]{figs/ghs-g-ghs}
%%   \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
%% \end{figure}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Remove one of, or make a note of, the two curves for this
      work}\fixme{Fix MC issue here (volume wrong?)} \fixme{Add backward curve
      for this work mc?}The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when $\rr_1$
    and $\rr_2$ are in contact.  The color plot on the left shows the triplet
    distribution function, with white corresponding to the contact value of the
    \emph{pair} distribution function.  The plot on the right shows the value of
    $g^{(3)}$ along the path shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution}
\end{figure*}
